{\steve}: A hierarchical Bayesian model for Supernova Cosmology

### 2019-02-01 papers/methods/figures/tikz.tex
More figure changes

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{tikz}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
\usetikzlibrary{bayesnet}
\usetikzlibrary{external}
\tikzexternalize % activate!
\tikzset{external/force remake}
\begin{document}
	\begin{tikzpicture}
	% Obs nodes
	\node[obs]  (obssum) {$\hat{m}_B, \hat{x}_1, \hat{c}, \hat{\mathcal{C}}_\eta^{-1}$};
	\node[obs, left=0.8cm of obssum]  (zobs) {$\hat{z}$};
	\node[obs, right=0.6cm of obssum]  (mobs) {$\hat{m}$};
	\node[obs, right=0.6cm of mobs]  (pobs) {$\hat{p}$};
	% Latent nodes
	\node[det, above=of obssum, xshift=0.5cm] (sum) {$m_B, x_1, c$};
	\node[det, above=of zobs] (z) {$z$};
	\node[det, above=of mobs] (m) {$m$};
	\node[det, above=of pobs, yshift=0.449cm] (p) {$p$};	
	\node[det, above=of z] (mu) {$\mu$};
	\node[latent, right=4.1cm of mu] (MBobs) {$M_B, x_1^*, c^*$};
	% Survey nodes
	\node[latent, above=of sum, yshift=0.3cm, xshift=1.4cm, text width=1.85cm, align=center] (pop1) {$\langle x_1^i \rangle, \langle c^i \rangle,\sigma_{M_B}, $\\$ \sigma_{x_1}, \sigma_c, \alpha_c$ };

	\node[latent, left=1.3cm of pop1, align=center] (kappa) {$\kappa_0, \kappa_1$};
	% Global nodes
	\node[latent, above=2.1cm of mu]  (cosmo) {$\Omega_m, w$};
	\node[latent, above=2.1cm of MBobs, xshift=0.8cm, align=center]  (ab) {$\langle M_B \rangle$};
	\node[latent, right=0.1cm of cosmo, align=center]  (dz) {$\delta \mathcal{Z}_i$};
	\node[latent, right=0.1cm of dz, align=center] (dd) {$\alpha, \beta, \delta(0)$, \\$\delta(\infty)$};
	% Connect the nodes
	\edge {sum, dz, kappa} {obssum};
	\edge {z} {zobs};
	\edge {m} {mobs};
	\edge {p} {pobs};
	\edge {z,cosmo} {mu};
	\edge {pop1, ab} {MBobs};	
	\edge {mu, MBobs, m, p, dd} {sum};

	% Plates
	\plated[thick] {sn} {(obssum)(zobs)(mobs)(pobs)(sum)(z)(mu)(MBobs)} {$\forall\ \rm{SN}$} ;
	\plated[thick] {survey} {(sn)(pop1)(kappa)} {\\$\forall\ \rm{Survey}$} ;
	\end{tikzpicture}
\end{document}

>>>>

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{tikz}
\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
\usetikzlibrary{bayesnet}
\usetikzlibrary{external}
\tikzexternalize % activate!
\tikzset{external/force remake}
\begin{document}
	\begin{tikzpicture}
	% Obs nodes
	\node[obs]  (obssum) {$\hat{m}_B, \hat{x}_1, \hat{c}, \hat{\mathcal{C}}_\eta^{-1}$};
	\node[obs, left=0.8cm of obssum]  (zobs) {$\hat{z}$};
	\node[obs, right=0.6cm of obssum]  (mobs) {$\hat{m}$};
	\node[obs, right=0.6cm of mobs]  (pobs) {$\hat{p}$};
	% Latent nodes
	\node[det, above=of obssum, xshift=1.2cm] (mb) {$m_B$};
	\node[latent, left=of mb, xshift=0.1cm] (x1c) {$x_1, c$};
	\node[det, above=of zobs] (z) {$z$};
	\node[det, above=of mobs, yshift=-0.5cm] (m) {$m$};
	\node[det, above=of pobs, yshift=0.5cm] (p) {$p$};	
	\node[det, above=of z] (mu) {$\mu$};
	\node[latent, above=of p, yshift=-0.5cm] (MB) {$M_B$};
	% Survey nodes
	\node[latent, above=of x1c, yshift=0.9cm, xshift=-0.65cm, align=center] (pop1) {$\langle x_1^i \rangle, \langle c^i \rangle, $\\$ \sigma_{x_1}, \sigma_c, \alpha_c$ };

	\node[latent, right=0.2cm of pop1, align=center] (kappa) {$\kappa_0, \kappa_1$};
	% Global nodes
	\node[latent, above=2.1cm of mu]  (cosmo) {$\Omega_m, w$};
	\node[latent, above=1.8cm of MB, xshift=0cm, align=center]  (MBpop) {$\langle M_B \rangle,$ \\ $\sigma_{M_B}$};
	\node[latent, right=1.43cm of cosmo, align=center]  (dz) {$\delta \mathcal{Z}_i$};
	\node[latent, right=0.1cm of dz, align=center] (ab) {$\alpha, \beta, \delta(0)$, \\$\delta(\infty)$};
	% Connect the nodes
	\edge {mb, x1c, dz, kappa} {obssum};
	\edge {z} {zobs};
	\edge {m} {mobs};
	\edge {p} {pobs};
	\edge {z,cosmo} {mu};
	\edge {MBpop} {MB};	
	\edge {MB, mu, ab, m, p, x1c} {mb}
	\edge {pop1, z} {x1c};

	% Plates
	\plated[thick] {sn} {(mb)(obssum)(zobs)(mobs)(pobs)(x1c)(z)(mu)(MB)(m)(p)} {$\forall\ \rm{SN}$} ;
	\plated[thick] {survey} {(sn)(pop1)(kappa)} {\\$\forall\ \rm{Survey}$} ;
	\end{tikzpicture}
\end{document}

### 2019-02-01 papers/methods/paper.tex
More figure changes

 \begin{figure}
 	\begin{center}
 		\includegraphics[width=\columnwidth]{tikz-figure0.pdf}
 	\end{center}
 	\caption{Probabilistic graphical model for our likelihood \added{without selection effects}. Double-lined nodes represent observed variables, diamond nodes represent deterministic variables, single-lined ellipse nodes represent fit variables. The SN box represents observed variables and latent variables for each individual supernova, whilst the survey box represents survey-specific variables, which in general describe the supernova population for the survey and the systematics associated with it. Variables that appear outside both boxes represent top level model parameters. \added{We note that we have shown the model to have latent variables $\lbrace M_B,\,x_1\,c\rbrace$, which uniquely determines $\lbrace m_B,\,x_1\,c\rbrace$, given $\mu$ and other parameters. Thus, conceptually the two nodes make up a single layer in our hierarchy, not two layers. In the code implementation, $m_B$ is more efficient parametrise instead of $M_B$, however the mathematics remains constant regardless of if you parametrise $M_B$ or $m_B$ as one can determine the other.}}
 	\label{fig:pgm}
 \end{figure}

>>>>

 \begin{figure}
 	\begin{center}
 		\includegraphics[width=\columnwidth]{tikz-figure0.pdf}
 	\end{center}
 	\caption{Probabilistic graphical model for our likelihood \added{without selection effects}. Double-lined nodes represent observed variables, diamond nodes represent deterministic variables, single-lined ellipse nodes represent fit variables. The SN box represents observed variables and latent variables for each individual supernova, whilst the survey box represents survey-specific variables, which in general describe the supernova population for the survey and the systematics associated with it. Variables that appear outside both boxes represent top level model parameters. \added{We note that we have shown the model to have latent variables $\lbrace M_B,\,x_1\,c\rbrace$, which uniquely determines $m_B$, given $\mu$ and other parameters. Thus, the two nodes $M_B$ and $m_B$, make up a single layer in our hierarchy, not two layers. In the code implementation, $m_B$ is more efficiently parametrised instead of $M_B$, however the mathematics remains constant regardless of if you parametrise $M_B$ or $m_B$ as one can determine the other. Finally, as we take redshift measurement $\hat{z}$, mass probability $\hat{m}$ and classification probability $\hat{p}$ as exact they are not conditioned on underlying distributions and are top level parameters. We add the deterministic $m$ and $p$ nodes in our diagram for clarity, however as they have a one-to-one mapping onto $\hat{m}$ and $\hat{p}$ respectively we simply use the observed values in the mathematics of the rest of the paper.}}
 	\label{fig:pgm}
 \end{figure}
